\documentclass[letterpaper,10pt]{article}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage[table,dvipsnames]{xcolor}
\usepackage{charter}
\usepackage[colorlinks=true,linkcolor=blue,urlcolor=blue,citecolor=blue]{hyperref}


% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}
\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0.1in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that the generated PDF is machine readable/ATS parsable.
\pdfgentounicode=1

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \vspace{-2pt}\textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.0\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

% Compact single-line description (no extra indent) used for short sections like Volunteering
\newcommand{\resumeBrief}[1]{\vspace{-4pt}\begin{itemize}[leftmargin=0.0in,label={}]\item\small{#1 \vspace{-2pt}}\end{itemize}\vspace{-5pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\huge \scshape Vaishnavi Poti} \\ \vspace{5pt}
    \small
    \href{https://github.com/skycypherxo}{github.com/skycypherxo} $|$ \href{https://www.linkedin.com/in/vaishnavi-v-p/}{linkedin.com/in/vaishnavi-v-p/} $|$ \href{mailto:potivaishnavi21@gmail.com}{potivaishnavi21@gmail.com}
    \vspace{-8pt}
\end{center}

% Education
\section{Education}
    \resumeSubHeadingListStart
        \resumeSubheading
            {University of Mumbai -- Thadomal Shahani Engineering College}{Expected: June 2026}
            {Bachelor of Engineering (Artificial Intelligence and Data Science)   (Current GPA: 8.83 / 10)}{Mumbai}
            \resumeItemListStart
                \resumeItem{Computer Networks, Operating Systems,  Database Management, Deep Learning, NLP}
            \resumeItemListEnd

        \resumeSubheading
            {S.I.E.S College of Arts, Science and Commerce}{March 2022}
            {Higher Secondary School Certificate (Percentage: 86.5)}{Mumbai, India}
            \resumeItemListStart
                \resumeItem{Courses: Computer Science, Physics, Chemistry, Mathematics}
            \resumeItemListEnd

        \resumeSubheading
            {Swami Vivekanand High School }{March 2020}
            {Secondary School Certificate   (Percentage: 93.4)}{Mumbai, India}
    \resumeSubHeadingListEnd

% Internships
\section{Internships}

\resumeSubHeadingListStart
\resumeSubheading
    {Government of Maharashtra}{November 2024 -- May 2025 \href{https://drive.google.com/file/d/1qbBfanYD9CQLAFl07efEwsPnJ0FCqHbV/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}}
    {Web Team Lead and Fullstack Developer }{Mumbai}
  \resumeItemListStart
    \resumeItem{Led a team of 8 to build the digital platform for the Maha CSR Summit 2025, including a real-time slot booking system, payment integration and automation.}
    \resumeItem{Architected and deployed scalable backend systems using AWS Amplify, DynamoDB, and Route 53, ensuring reliability during high-traffic event periods.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


    \resumeSubHeadingListStart
        \resumeSubheading
            {Dalsey, Hillblom and Lynn (DHL)}{June 2024 -- July 2024 \href{https://drive.google.com/file/d/1dtPS6S_dDL82myHAHvV0trkt0f50VSxs/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}}
            {Data Analytics Intern }{Andheri, Mumbai}
              \resumeItemListStart
    \resumeItem{Built interactive Power BI dashboards to analyze delivery efficiency, route performance, and operational cost metrics across regions.}
    \resumeItem{Automated reporting workflows using Power Automate, improving operational visibility and contributing to a 15\% efficiency increase.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
    

    \resumeSubHeadingListStart
        \resumeSubheading
            {Outlier AI}{Part-Time, 2023 -- 2024}
            {RLHF Trainer}{Remote}
  \resumeItemListStart
    \resumeItem{Evaluated and refined model outputs across text and multimodal tasks using Reinforcement Learning from Human Feedback (RLHF).}
    \resumeItem{Provided structured annotations and comparative scoring to improve reasoning, alignment, and user-response quality.}
  \resumeItemListEnd
    \resumeSubHeadingListEnd

% Skills
\section{Skills}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Frameworks}: React.js, Next.js, Flask}
    \resumeItem{\textbf{Languages and Technologies}: Python, JavaScript (JS), C, Java, HTML, CSS}
    \resumeItem{\textbf{Databases}: MySQL, MongoDB, Firebase, Pinecone, DynamoDB}
    \resumeItem{\textbf{Platforms}: GitHub, Firebase}
    \resumeItem{\textbf{Version Control}: Git}
    \resumeItem{\textbf{CI/CD}: GitHub Actions, AWS Amplify}
    \resumeItem{\textbf{ML Frameworks}: Tensorflow, Pytorch, Scikit-Learn, Hugging Face, Langchain, LangGraph}
    \resumeItem{\textbf{Tools}: Power BI, Power Automate, Kali Linux (Burpsuite, Nmap, SQLmap)}
\resumeSubHeadingListEnd

% Projects
\section{Projects}
 \resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{\normalsize{Multi-Agent System for Adaptive Production Scheduling}} $|$ \emph{LangChain, LangGraph, CrewAI, Python}}{}
  \resumeItemListStart
    \resumeItem{Developed and compared three multi-agent architectures (pure Python, LangChain, CrewAI/LangGraph) for dynamic job scheduling and resource allocation.}
    \resumeItem{Implemented custom agent communication protocols, role-based agent teams, and adaptive state routing to handle delays, machine downtime, and priority shifts.}
    \resumeItem{Benchmarked throughput, idle time, and rescheduling latency to evaluate performance trade-offs across each MAS design.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{\normalsize{Custom University-Specific Small Language Model (SLM)}} $|$ \emph{Python, NumPy}}{}
  \resumeItemListStart
    \resumeItem{Built a transformer-based Small Language Model entirely from first principles, including custom tokenizer, attention layers, and gradient updates.}
    \resumeItem{Trained on curated university-specific datasets to answer academic, admission, and campus-related queries with improved contextual accuracy.}
    \resumeItem{Achieved higher relevance and reduced hallucination compared to retrieval-only baselines.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{\normalsize{InkChat}} $|$ \emph{Next.js, TypeScript, WebSockets}}{}
  \resumeItemListStart
    \resumeItem{Developed a real-time collaborative whiteboard with simultaneous drawing, annotation, and chat interactions.}
    \resumeItem{Implemented synchronized canvas updates with low-latency WebSocket communication for multi-user consistency.}
    \resumeItem{Optimized rendering and data flow to ensure smooth performance during large collaborative sessions.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{\normalsize{Farmissan}} $|$ \emph{React.js, Firebase}}{}
  \resumeItemListStart
    \resumeItem{Built a farm-to-consumer marketplace enabling direct sales and improved revenue for producers.}
    \resumeItem{Implemented real-time product listings, geolocation-based discovery, and secure authentication/workflows using Firebase services.}
    \resumeItem{Added review and feedback features to increase trust and improve repeat user engagement.}
  \resumeItemListEnd
\resumeSubHeadingListEnd

\section{Extracurriculars}
\resumeSubHeadingListStart

\resumeSubheading
  {AceRyx}{Sept 2025 -- Present}
  {Lead Founder \& Developer}{Remote}
  \resumeItemListStart
    \resumeItem{Found and lead a services platform offering custom website development, chatbot solutions, and digital consulting services.}
    \resumeItem{Spearhead end-to-end project delivery from client consultation to implementation, focusing on tailored AI-driven solutions.}
  \resumeItemListEnd

\resumeSubheading
  {NeedForCode 3.0 Hackathon (Winner)}{Aug 2024 \href{https://drive.google.com/file/d/1QR37vOQbHarbMVUUH1puT4XijyL6CXyl/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}}
  {National Level Hackathon}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Led development of \textit{DigiDaani}, a MERN-based ration distribution platform with real-time inventory tracking.}
    \resumeItem{Implemented secure authentication and 360° face verification using MediaPipe to prevent identity misuse.}
  \resumeItemListEnd

\resumeSubheading
  {Codeissance (First Runner-Up)}{Sept 2024 \href{https://drive.google.com/file/d/1RGGVdqPzF1qS2lTrbA7_dj5S3q346h4I/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}}
  {National Level Hackathon}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Built \textit{Place-U}, a placement and interview-preparation platform with ML-driven interview feedback and resume scoring.}
    \resumeItem{Implemented mock interview simulations, chatbot workflows, and resume-builder modules.}
  \resumeItemListEnd

\resumeSubheading
  {AI Challenge (Second Place)}{Sept 2024 \href{https://drive.google.com/file/d/1w0XUHqwf17X3AeM54GCIYUw1k6YuKAd6/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}}
  {National Level Hackathon}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Created analytical dashboards and cybersecurity risk assessment reports highlighting AI-driven anomaly detection.}
  \resumeItemListEnd

\resumeSubheading
  {Picture This Photography Competition}{March 2024}
  {First Runner-Up}{Mumbai, India}
  \resumeItemListStart
    \resumeItem{Secured first runner-up position in competitive photography contest showcasing creative vision and technical photography skills.}
  \resumeItemListEnd

\resumeSubHeadingListEnd


\section{Volunteering}
\resumeSubHeadingListStart

\resumeSubheading
  {Science O Mania, Exhibition Fair}{Nov 2025}
  {Student Mentor}{Mumbai, India}
  \begin{itemize}[leftmargin=1.8em, label={--}]
    \item Guided Grade 12 students in developing a hardware-based soil monitoring and analysis system for the exhibition.
  \end{itemize}

\resumeSubheading
  {Social Media Bots }{2023 -- 2024}
  {Developer}{Remote}
  \begin{itemize}[leftmargin=1.8em, label={--}]
    \item Developed and maintained scalable automation bots for Discord and Reddit communities serving 23M+ collective users.
  \end{itemize}

\resumeSubheading
  {InAmigos Foundation}{\href{https://drive.google.com/file/d/1Kmgj9lRByNkx7EB3o7pfIt0a6cJ9eTru/view?usp=drive_link}{\textcolor{blue}{[Certificate]}}} 
  {Volunteer}{Mumbai, India}
  \begin{itemize}[leftmargin=1.8em, label={--}]
    \item Assisted in planning and executing social welfare programs supporting marginalized communities.
  \end{itemize}

\resumeSubheading
  {Ratna Nidha Charitable Trust}{} 
  {Book Collection Drive Organizer}{Mumbai, India}
  \begin{itemize}[leftmargin=1.8em, label={--}]
    \item Led a community-driven book donation initiative to expand educational access for underprivileged students.
  \end{itemize}

\resumeSubHeadingListEnd


% -----------RELATED COURSEWORK AND CERTIFICATES-----------
\section{Related Coursework and Certificates}
\resumeSubHeadingListStart
    \resumeSubheading{Certificates}{}{}{}
    \resumeItemListStart
    \resumeItem{\href{https://drive.google.com/file/d/1eRMrkQsVajNq8gmjKuh5S0TzYjHSdl7L/view}{Stock Market and Finance}}
    \resumeItem{\href{https://drive.google.com/file/d/1wAHCC7eUFHxw6MSohqXeQE-LyX5rhF1G/view}{Python Programming}}
    \resumeItem{\href{https://drive.google.com/file/d/1knJCjygqzEXNLz81BkYtJ9mMH8AjFFw6/view}{Web Development}}
    \resumeItem{\href{https://drive.google.com/drive/folders/1vBEMoLjvOWieMp81bUmmTmJtVjrxEBoF}{Data Analytics with Python}}
    \resumeItem{\href{https://www.cloudskillsboost.google/public_profiles/d5634d36-991d-4605-af7e-1bc91d882319}{Google Cloud}}
    \resumeItemListEnd
\resumeSubHeadingListEnd

% -----------ADDITIONAL SKILLS-----------
\section{Additional Skills}
\resumeSubHeadingListStart
    \resumeItem{\textbf{Languages}: Languages: English, Hindi, Marathi, Kannada, Tulu (fluent); Conversational French}
    \resumeItem{\textbf{Martial Arts}: Winner of multiple national and international level karate championships; Dan 1 Black Belt holder}
\resumeSubHeadingListEnd

\end{document}

